---
title: "Final Exercise for Software Carpentry Workshop"
author: "Andrés Morera"
date: "April 1, 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
**Exercise Instructions:**

Take a look at the gapminder data, and pick three countries you are interested in.  Write an Rmd script to load the data file, select all the data fr that country (hint: use subset() function or dplyr), and use plot() to make three scatter plots (one for each country) that has year on the x-axis and GDP on the y-axis.  Label axes and give the graph a title.  Make sure you load all the libraries you might need.  Describe any trends you see for each country using markdown text.

**Procedure:**

1. Load the libraries I might need. 

```{r} 
library("dplyr", lib.loc="~/R/x86_64-pc-linux-gnu-library/3.2")
```

2. Get the data into an object I can actually use.

```{r}
gap.data <- read.csv(file = "/home/andeerz/Desktop/SWC_2016_Cyverse_Demo/gapminder_stuff/gapminder.csv")

```

3. Get the th

plot(gap.data$year[gap.data$country %in% c("Spain","Mongolia","Zimbabwe")], gap.data$gdpPercap[gap.data$country %in% c("Spain","Mongolia","Zimbabwe")], main= "Per Capita GDP of Three Interesting Countries!", xlab= "Year", ylab= "Per Capita GDP ($US)", col= c("red", "blue", "green"))


